### 2022-08-02 main/chapter_2ljets.tex
write validation; add intro sentence for unblinding

\subsection{Leptons}
In the context of $\twoljets$, `leptons' means `electron-or-muons';
this is because taus, which decay before reconstruction, and are not used
directly in $\twoljets$, and neutral leptons (the neutrinos) go missing.

@@

In an apparent notional effort to address this problem, we treat the signal
cross-section specially by not fitting it within a constraint, but fixing it
to central, up, and down values for three repeated analyses.
We then derive and report separate exclusion contours for each cross-section
variation;
such alternative contours are shown as the three observed limits
in Figures~\ref{fig:2ljets_contours_c1n2} and~\ref{fig:2ljets_contours_gmsb}.
This approach is entirely standard, and is indeed ingrained into \histfitter\
through the special parameter name
\texttt{$(\alpha\_)$SigXSec}~\cite{histfitter2014, histfittergithub}.

@@

\section{Validation}
\label{sec:2ljets_validation}
Figure~\ref{fig:2ljets_low_crz_extensions}
Figure~\ref{fig:2ljets_splits}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_aux_CR_Z_met_EWK_met_Sign.pdf}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_aux_CR_Z_met_EWK_met_Et.png}
\caption{}
\end{subfigure}
\caption[
Extension from CR-Z into higher $\metsig$ and $\met$
]{%
Extension from CR-Z into higher (a) $\metsig$ and (b) $\met$.
The arrow indicates the CR-Z  upper bound of $\metsig$; it has no hard
upper bound of $\met$.
Systematic uncertainties are extrapolated from CR-Z to the extended tail.
The tail overlaps with other regions, but shows good agreement with data.
Sub-figure (b) is reproduced from auxiliary material to the
paper~\cite{atlas2022searches}.
Each last bin includes overflow.
}
\label{fig:2ljets_low_crz_extensions}
\end{figure}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_splits_met_Sign_CRZZ.png}
\caption{CR-VZ, diboson}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_splits_met_Sign_CRZ.png}
\caption{CR-Z, $\zjets$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_splits_met_Sign_CRtt.png}
\caption{CR-tt, rare top}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_splits_met_Sign_SRllbb.png}
\caption{\srllbb, rare top}
\end{subfigure}
\caption[
Subcomponents of diboson, $\zjets$ and rare top processes.
]{%
Subcomponents of (a) diboson, (b) $\zjets$ and (c, d) rare top processes.
Target samples broken down by simulated sample identity codes.
The large three-lepton component in CR-VZ motivated its renaming from CR-ZZ.
The `no filter' selection comprises $\zjets$ samples with unconstrained jet
flavour.
Errors are statistical.
}
\label{fig:2ljets_splits}
\end{figure}

\section{Unblinding}
\label{sec:2ljets_unblinding}
Figure~\ref{fig:2ljets_prepre}
Figure~\ref{fig:2ljets_summary_unblinding}

>>>>

\subsection{Leptons}
\label{sec:2ljets_events_leptons}
In the context of $\twoljets$, `leptons' means `electron-or-muons';
this is because taus, which decay before reconstruction, and are not used
directly in $\twoljets$, and neutral leptons (the neutrinos) go missing.

@@

In an apparent notional effort to address this problem, we treat the signal
cross-section specially by not fitting it within a constraint, but fixing it
to central, up, and down values for three repeated analyses.
We then derive and report separate exclusion contours for each cross-section
variation;
such alternative contours are shown as the three observed limits
in Figures~\ref{fig:2ljets_contours_c1n2} and~\ref{fig:2ljets_contours_gmsb}.
This approach is entirely standard, and is indeed ingrained into \histfitter\
through the special parameter name
\texttt{SigXSec}~\cite{histfitter2014, histfittergithub}.

@@

\section{Validation}
\label{sec:2ljets_validation}
Many additional validation studies supported the $\twoljets$ search prior to
its publication.
Many of these, comprising hundreds of histograms in various regions or looser
selections in various event variables, are available to \atlas\ members in
our internal documentation~\cite{twoljets2018int}.
This section highlights some interesting results from these validation studies.

\paragraph{CR-Z-met}
Concerns about our modelling of $\zjets$ and diboson backgrounds have been
raised due to our deficits in SR-Low and SR-High, which compound with the
anticipated difficulty in modelling the $\met$ tails of $\zjets$.
To further check these backgrounds, Figure~\ref{fig:2ljets_low_crz_extensions}
displays histograms in a `CR-Z-met', which is modifies CR-Z
(from Table~\ref{tab:2ljets_low}) by removing its upper bound on $\metsig$.
The arrow in Figure~\ref{fig:2ljets_low_crz_extensions_metsig} indicates this
upper bound at $\metsig = 9$, and shows excellent agreement with data across
the entire distribution, both where $\zjets$ dominates and where diboson
dominates.
The corresponding $\met$ distribution that is shown in
Figure~\ref{fig:2ljets_low_crz_extensions_met}
similarly shows excellent agreement.

Like our other plots intended for publication, these figures use the full fit
model with all variations for statistical and systematic uncertainties,
and are fitted to data in control and signal regions, but the signal regions
have little effect since the pulled variations are normalized to this control
region.
To avoid the work of evaluating variations in CR-Z-met (and all of its bins),
its variations are linearly extrapolated from CR-Z.

Good modelling in CR-Z-met is a positive sign for our simulations prior to
their modification in the fit.
Noting that CR-Z excludes $m(W)$, however, this does not conflict with the idea
of poor modelling in the signal regions.

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_aux_CR_Z_met_EWK_met_Sign.pdf}
\caption{}
\label{fig:2ljets_low_crz_extensions_metsig}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_aux_CR_Z_met_EWK_met_Et.png}
\caption{}
\label{fig:2ljets_low_crz_extensions_met}
\end{subfigure}
\caption[
Extension from CR-Z into higher $\metsig$ and $\met$
]{%
Extension from CR-Z into higher (a) $\metsig$ and (b) $\met$.
The arrow indicates the CR-Z  upper bound of $\metsig$; it has no hard
upper bound of $\met$.
Systematic uncertainties are extrapolated from CR-Z to the extended tail.
The tail overlaps with other regions and shows good agreement with data.
Sub-figure (b) is reproduced from auxiliary material to the
paper~\cite{atlas2022searches}.
Each rightmost bin includes overflow.
}
\label{fig:2ljets_low_crz_extensions}
\end{figure}

\paragraph{Sub-processes}
\TODO{sort out top other label}
Our high-level sample labels such as $\ttbar$, $\zjets$, diboson and
rare-top (`Top other') each include many sub-samples that are physically
distinct and non-interfering.
Highlights from a study of the contributions from these sub-samples are
presented in Figure~\ref{fig:2ljets_splits}.

Although it might be expected that our $Z$-like two-lepton selection would
favour the $ZZ$-like diboson sub-sample, with the other $Z$ decaying to
neutrinos,
Figure~\ref{fig:2ljets_splits_diboson} shows that in fact the three-lepton
$WZ$-like process has almost equal yields.
All of those $WZ$ events therefore have a missing third lepton, that could be
softer than the few $\eV[G]$ needed for our baseline selection
(see Section~\ref{sec:2ljets_events_leptons}),
or outside of our angular acceptance.
(Overlap removal cannot explain this since we count baseline leptons before
it.)
Although we would hope that such failed identifications would be rare,
the effect is enhanced by the fact that $WZ$ has a larger cross-section than
$ZZ$ by around a factor of three~\cite{Campbell:2011bn}, that is enhanced
by the sum over $W^+Z$ and $W^-Z$ processes.

Our \sherpa\ diboson samples include the interference of electroweak processes
for each fixed final state, so for example the separation of $ZZ$ and $WW$ is
not exact since they interfere.
These histograms are therefore split on charged lepton number in their
final states.

Some of our $\zjets$ samples are filtered by hadron flavour
(requiring at least one selected hadron with $|\eta| < 4$), and
Figure~\ref{fig:2ljets_splits_zjets} shows CR-Z with its $\zjets$ yields
split by these filters.
Heavy flavour samples are enhanced, with the filtered yields comprising
$22\%$ bottom and $30\%$ charm flavours despite the $\nbtag = 0$ veto in CR-Z;
this is sensible, since we also require $\met$, and extra non-prompt $\met$ is
generated  in the weak decays of of heavy-flavoured hadrons.

The remaining parts of Figure~\ref{fig:2ljets_splits_diboson} show that
of the rare-top sample, $\ttbar Z$ is the largest contribution,
at $73\%$ in \srllbb, but that contributions from other rare processes
such as $tW\kern-0.4exZ$, $t\ell\ell g$ and $\ttbar W$ are significant.
Here, the plain `Top other' label refers to all other rare-top contributions.

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_splits_met_Sign_CRZZ.png}
\caption{CR-VZ, diboson}
\label{fig:2ljets_splits_diboson}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_splits_met_Sign_CRZ.png}
\caption{CR-Z, $\zjets$}
\label{fig:2ljets_splits_zjets}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_splits_met_Sign_CRtt.png}
\caption{CR-tt, rare top}
\label{fig:2ljets_splits_topother1}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_splits_met_Sign_SRllbb.png}
\caption{\srllbb, rare top}
\label{fig:2ljets_splits_topother2}
\end{subfigure}
\caption[
Subcomponents of diboson, $\zjets$ and rare top processes.
]{%
Subcomponents of (a) diboson, (b) $\zjets$ and (c, d) rare top processes.
Target samples broken down by simulated sample identity codes.
The large three-lepton component in CR-VZ motivated its renaming from CR-ZZ.
The `no filter' selection comprises $\zjets$ samples with unconstrained jet
flavour.
Errors are statistical.
}
\label{fig:2ljets_splits}
\end{figure}

\section{Unblinding}
\label{sec:2ljets_unblinding}
This section is not a discussion of our unblinded results.
It is a discussion of our unblinding procedures,
their extent, their implementation, and their effect on the results.

Figure~\ref{fig:2ljets_prepre}
Figure~\ref{fig:2ljets_summary_unblinding}
